Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-26 papers/LREC2020/lrec2020naming.tex
added authors to LREC paper

\name{Author1, Author2, Author3}

\address{Affiliation1, Affiliation2, Affiliation3 \\
         Address1, Address2, Address3 \\
         author1@xxx.yy, author2@zzz.edu, author3@hhh.com\\
         \{author1, author5, author9\}@abc.org\\}

>>>>

\name{Carina Silberer, Sina Zarrie\ss, Gemma Boleda}

\address{Universitat Pompeu Fabra, University of Jena, Universitat Pompeu Fabra \\
         Barcelona (Spain), Jena (Germany), Barcelona (Spain) \\
         sina.zarriess@uni-jena.de\\
         \{carina.silberer, gemma.boleda\}@upf.edu\\}
